Decomposing labelled proof theory for intuitionistic modal logic

### 2019-08-31 caleidoscope/caleidoscope.tex
working on extensions section

Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
%
These systems enjoy cut-elimination via usual arguments. Proofs of the the axioms we mentioned are below:

@@

The generality of the result adds a new rule to the system $\labIKp$ in order to capture the \emph{Scott-Lemmon axiom} or \emph{$\agklmn$ axiom}: 
\begin{center}
	$\lozenge^{k} \square^{l} A \IMP \square^{m}\lozenge^{n} A$
\end{center}
Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:

@@

See this axiom in the Figure~\ref{fig:gklmn} \todo{Wrong label. why??}

@@

>>>>

Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
%
These systems enjoy cut-elimination via usual arguments. Proofs of the axiom mentioned for $\DIA$ and $\BOX$ are below:

@@

Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A$ (Figure \ref*{fig:gklmn}).\todo{Wrong label. why??}

Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:

@@

@@

Following the idea to have a sound and complete system adding the axiom $\agklmn$ to the system $\labIKp$, we introduce the next rule:

\begin{center}
	$\vlderivation { \vlin {\gklmn}{y', u$ fresh$}{\B, xR^{k}y, xR^{m}z, \Left \Rightarrow \Right}{\vlhy {\B, y \le y', xR^{k}y, xR^{m}z, y'R^{l}u, zR^{n}u, \Left\Rightarrow \Right}}}$
\end{center}

We start proving that our new system is complete with the base case of $\mathsf{k = l = m = n = 1}$:

\begin{theorem}
	The system $\labIKp +\agklmn$ is complete for $\mathsf{k = l = m = n = 1}$.
\end{theorem}

\begin{proof}
	\begin{center}
		\scalebox{0.93}{
			$\vlderivation {\vlin {\sir}
				{y$ fresh$}
				{\Rightarrow x \colon \lozenge \square A \vljm \square \lozenge A}
				{\vlin {\sbr}
					{z, w $ fresh $}
					{x \le y, y \colon \lozenge \square A \Rightarrow y \colon \square \lozenge A}
					{\vlin {\sdl}
						{u$ fresh$}
						{x \le y, y \le z, zRw, y \colon \lozenge \square A \Rightarrow w \colon \lozenge A}
						{\vlin {\ftwo}
							{t$ fresh$}
							{x \le y, y \le z, zRw, yRu, u \colon \square A \Rightarrow w \colon \lozenge A}
							{\vlin {\gklmn}
								{t', j$ fresh$}
								{x \le y, y \le z, u \le t, zRw, yRu, zRt, u \colon \square A \Rightarrow w \colon \lozenge A}
								{\vlin {\sdr}
									{}
									{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A}
									{\vlin {\trans}
										{}
										{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A, j \colon A}
										{\vlin {\sbl}
											{}
											{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A, j \colon A}
											{\vlin {\refl}
												{}
												{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A, j \colon A \Rightarrow w \colon \lozenge A, j \colon A}
												{\vlin {\ids}
													{}
													{x \le y, y \le z, u \le t, t \le t', u \le t',j \le j, zRw, yRu, zRt, t'Rj, wRj, u \colon \square A, j \colon A \Rightarrow w \colon \lozenge A, j \colon A}
													{\vlhy {}}}}}}}}}}}}$}
	\end{center}
\end{proof}

In order to have a completeness proof for the general case, we need to introduce the rules from the Lemma~\ref{lemma:admis}.

\begin{lemma}\label{lemma:admis} The following rules are admissible in $\labIKp$:
	\begin{enumerate}
		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, x \colon \square^{k} A\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, x \colon \square^{k} A, z \colon A \Rightarrow \Right}}}$}
		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, x \colon \square^{k} A}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, y \colon A}}}$}
		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, x \colon \lozenge^{k} A \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, y \colon A \Rightarrow \Right}}}$ }
		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, x \colon \lozenge^{k}A}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, x \colon \lozenge^{k}A, y \colon A}}}$}
	\end{enumerate}
	%\textbf{Probably F2g???}
\end{lemma}

Our conjecture is that it is possible to prove completeness of the system for the general case by induction in the $k$ parameter. This proof is ongoing study.
